Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-01-18 README.Rmd
initial commit
gpl3

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# Robinson2020

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Dendrochronological dates confirm a Late Prehistoric population decline in the American Southwest derived from radiocarbon dates"
```

# robinson2020

@@

> Robinson, Erick, R. Kyle Bocinsky, Jacob Freeman, Darcy Bird, Robert L. Kelly, (2020). _`r Title`_. Under review.

<!-- Our pre-print is online here: -->

<!-- > Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

@@

> Bocinsky, R. Kyle and Erick Robinson, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("bocinsky/robinson2020")
```
